Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks

### 2025-02-21 Phase_II/draft/GAN.tex
modification

\section{Generative Adversarial Networks}

In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs). The concept is rather simple, as it consists of two competing networks. The first network is called a Generator and creates new images based on an input image. Here, for consistency, the images generated by the Generator will be denoted as generated images. The second network is the Discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \cite{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

@@

where $D^{*}_{G}$ denotes the optimum of the Discriminator for a given fixed Generator and is expressed as

@@

It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.

@@

	\caption{Generator and Discriminator losses for three different learning rates. The upper figure shows the total Discriminator loss, and the lower figure shows the total generator loss. There is no significant difference, but the highest learning rate might be prone to outliers. }

@@

	\caption{Generator and Discriminator losses for three different kernel sizes in the convolutional layers. Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}

@@

Later, GAN extended its version to a conditional model \cite{mirza2014conditional}. In this case, both Generator and Discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) is expressed as:
		V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x|y) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
	\label{eq:conditional_GAN}

>>>>

\section{Generative Adversarial Networks}
In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs). The concept is rather simple, as it consists of two competing networks. The first network is called a Generator and creates new images based on an input image. Here, for consistency, the images generated by the Generator will be denoted as generated images. The second network is the Discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \cite{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

@@

where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator, shown in equation (\ref{eq:Disc_optimum}). It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}. 

@@

@@

	\caption{Generator and discriminator losses for three different learning rates. The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss. There is no significant difference, but the highest learning rate might be prone to outliers. }

@@

	\caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers. Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}

@@

Later, GAN extended its version to a conditional model \cite{mirza2014conditional}. In this case, both Generator and Discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) is expressed as:
\begin{equation}
	\centering
	\begin{aligned}
		V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x|y) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
	\end{aligned}
	\label{eq:conditional_GAN}
\end{equation}

### 2025-02-21 Phase_II/draft/ParaGan.tex
modification

\begin{figure*}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
	\end{subfigure}
	\caption{This set of figures shows the result of GAN for II. The left panels are signals using six baselines, which work as input for GAN. The first middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training. The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II. Due to the adversarial nature of GAN, where the Generator and Discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.

\subsection{Data Preparation}
First, we simulate fast-rotating stars, which are modeled as oblate spheroids with different radii and oblateness between 0.5 and 1. Different viewed angles have also been considered, with the effect of gravity darkening being linear dependence. The traced ellipses arise when integrating over the hour angle of the source. For the hyperparameter tuning and comparison of different telescopes, the total hour angle is about 11.5 hours. The ellipses are plotted and converted into grayscale images, resized, and stored as pure arrays to simplify further analysis. 
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
		\caption{The monopole.}
		\label{fig:mom1}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
		\caption{The centroids along x direction.}
		\label{fig:mom2}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
		\caption{The centroids along y direction.}
		\label{fig:mom3}
	\end{subfigure}\hfill
	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
	\label{fig:cen}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
		\caption{The 2nd order moment $\mu_{11}$.}
		\label{fig:mom4}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
		\caption{The 2nd order moment $\mu_{20}$.}
		\label{fig:mom5}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
		\caption{The 2nd order moment $\mu_{02}$.}
		\label{fig:mom6}
	\end{subfigure}\hfill
	\caption{The second-order central moments provide information about the size and shape of stellar objects. This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
	\label{fig:struc}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
		\caption{The 3rd order moment $\mu_{30}$.}
		\label{fig:mom7}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
		\caption{The 3rd order moment $\mu_{03}$.}
		\label{fig:mom8}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
		\caption{The 3rd order moment $\mu_{21}$.}
		\label{fig:mom9}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
		\caption{The 3rd order moment $\mu_{12}$.}
		\label{fig:mom10}
	\end{subfigure}\hfill
	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN. It calculates the skewness and evaluates the brightness distribution of images.}
	\label{fig:moments}
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
	\end{subfigure}
	\caption{This set of figures shows the result of GAN for II. The left panels are signals using six baselines, which work as input for GAN. The first middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training. The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II. Due to the adversarial nature of GAN, where the Generator and Discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.
\subsection{Data Preparation}
First, we simulate fast-rotating stars, which are modeled as oblate spheroids with different radii and oblateness between 0.5 and 1. Different viewed angles have also been considered, with the effect of gravity darkening being linear dependence. The traced ellipses arise when integrating over the hour angle of the source. For the hyperparameter tuning and comparison of different telescopes, the total hour angle is about 11.5 hours. The ellipses are plotted and converted into grayscale images, resized, and stored as pure arrays to simplify further analysis. 
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
		\caption{The monopole.}
		\label{fig:mom1}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
		\caption{The centroids along x direction.}
		\label{fig:mom2}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
		\caption{The centroids along y direction.}
		\label{fig:mom3}
	\end{subfigure}\hfill
	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
	\label{fig:cen}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
		\caption{The 2nd order moment $\mu_{11}$.}
		\label{fig:mom4}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
		\caption{The 2nd order moment $\mu_{20}$.}
		\label{fig:mom5}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
		\caption{The 2nd order moment $\mu_{02}$.}
		\label{fig:mom6}
	\end{subfigure}\hfill
	\caption{The second-order central moments provide information about the size and shape of stellar objects. This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
	\label{fig:struc}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
		\caption{The 3rd order moment $\mu_{30}$.}
		\label{fig:mom7}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
		\caption{The 3rd order moment $\mu_{03}$.}
		\label{fig:mom8}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
		\caption{The 3rd order moment $\mu_{21}$.}
		\label{fig:mom9}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
		\caption{The 3rd order moment $\mu_{12}$.}
		\label{fig:mom10}
	\end{subfigure}\hfill
	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN. It calculates the skewness and evaluates the brightness distribution of images.}
	\label{fig:moments}
\end{figure*}

### 2025-02-21 Phase_II/draft/Result.tex
modification

\section{The Reconstructed Image with GAN}

In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously. The best performance for image reconstruction has been observed with a learning rate of $2 \cdot 10^{-4}$, a kernel size of 5x5, and equal noise percentages in original and generated images. The batch size selected is 1, and the Discriminator-Generator receives equal training.

@@

\subsection{The Reconstructed Parameters for Object}
The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only. However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity with respect to the center of the source \citep{teague1980image}. These parameters based on the moments fully describe the two-dimensional ellipse that fits the image data.

>>>>

\section{The Reconstructed Image with GAN}
In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously. The best performance for image reconstruction has been observed with a learning rate of $2 \cdot 10^{-4}$, a kernel size of 5x5, and equal noise percentages in original and generated images. The batch size selected is 1, and the Discriminator-Generator receives equal training.

@@

\subsection{The reconstructed Parameters for object}
The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only. However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity with respect to the center of the source \citep{teague1980image}. These parameters based on the moments fully describe the two-dimensional ellipse that fits the image data.
